---
title: "R Notebook"
subtitle: "John-Henry Pezzuto"
output:
  pdf_document:
    latex_engine: xelatex
header-includes:
    - \usepackage{caption}
---
\captionsetup[table]{labelformat=empty}

## Load Packages & Data
```{r setup}
rm(list = ls())

library(tidyverse)
library(knitr)
library(kableExtra)
library(FactoMineR)
library(broom)
library(glmnet)
library(MultivariateRandomForest)
library(data.table)
theme_set(theme_minimal())
knitr::opts_chunk$set(include = FALSE, echo=FALSE, warning=FALSE, message=FALSE)

db <- read_csv("full_calculations.csv") %>% 
  select(-IPAddress, -X1,-(nostalgic:F_disgust)) %>%
  mutate_all(as.numeric)

survey.data <- read_csv("Delay Discounting_human_80.csv") 


```




```{r demographics}
respond.count <- survey.data %>% 
  select(Status) %>% 
  filter(!Status == "Survey Preview") %>% 
  count()
respond.count <- as.numeric(respond.count)
respond.count

female <- db$gender[which(db$gender==0)]
female <- sum(female == 0)
male <- db$gender[which(db$gender==1)]
male <- sum(male == 1)

## final sample size
final.samplesize <- nrow(db)

## age correlations 
age.min <- min(db$age, na.rm = TRUE)
age.max <- max(db$age, na.rm = TRUE)
```



```{r discount}


###########

factor.cols = db %>% select(ends_with("indifference.consistent"), average, average.consistent) %>% colnames(.)

patience.cols = c("Patience", "s.Patience", "td.Patience")

hyperbolic_exponential.cols = db %>% 
  select(ends_with(".k"), ends_with("exponential")) %>% 
  colnames(.)

beta.delta.cols = db %>% 
  select(ends_with(".beta"), ends_with(".delta")) %>% 
  colnames(.)

all.columns <- c(factor.cols, patience.cols, hyperbolic_exponential.cols, beta.delta.cols)
```


```{r PCA}
# pc <- PCA(db, graph = FALSE)
# pc$var$cor
# z <- pc$var

```



```{r essential}
db <- db %>% mutate_all(as.numeric)
db[is.na(db)] <- -1
```


```{r}
set.seed(8675309)
smp_size <- floor(0.70 * nrow(db))
train_ind <- sample(seq_len(nrow(db)), size = smp_size)


train <- db[train_ind, ]
test <- db[-train_ind, ]


train_x <- train %>% select(-one_of(all.columns))
train_x <- as.matrix(train_x)
train_y = train %>% select(one_of(all.columns))
train_y <- as.matrix(train_y)
test_x <- test %>% select(-one_of(all.columns))
test_x <- as.matrix(test_x)
test_y <- test %>% select(one_of(all.columns))
test_y <- as.matrix(test_y)
```

# Methods

## Participants
  Participants were `r respond.count` workers recruited from Amazon Mechanical Turk (MTurk). Participants were excluded from analysis if they did not complete the survey, had duplicate IP Addresses or MTurk IDs, failed a single attention check at the end of the survey, or reported not being able to read the questions in a comments section at the end of the survey. In addition we exclude participants who completed the survey in less than 6.5 minutes. This left us with a final sample size of  `r final.samplesize` (`r male` males, `r female` females) with an age range from `r age.min` to `r age.max`. Participants were required to answer all questions except for one section about private behavior. 

## Measures

  *Eliciting Discounting*. A total of 8 different methods were used the elicit discounting. All payments were hypothetical. These 8 different methods can be divided into two categories (speed-up and binary time discounting) that varied by both size of payment, and time period. In the speed-up measure, participants stated how much they would be willing to pay to speed up delivery of a hypothetical payment to a sooner time period. The payments began at $0.01 and ascended by \$2 increments in the smaller condition or by \$20 increments in the large condition until the full amount of the larger but later reward was reached. There were a total of 10 questions used by each method. Below is a table summarizing the 8 methods of eliciting discounting.



```{r full_names}
discountingtasksnames <- c("speedup.small.present, speedup.small.future, speedup.large.future, speedup.large.present, td.small.present, td.large.present, td.small.future, td.large.future")
discountingtasksnames <- unlist(strsplit(discountingtasksnames, ","))
discountingtasksnames <- str_replace_all(discountingtasksnames, fixed(" "), "")

###### 

taskname <- discountingtasksnames
taskname <- sort(as.character(taskname))
taskname <- str_replace(taskname, "td", "Time Discounting")
taskname <- str_replace_all(taskname, fixed("."), " ")
proper=function(x) paste0(toupper(substr(x, 1, 1)), tolower(substring(x, 2)))
taskname <- proper(taskname)

abbreviation <- c("slf", "slp", "ssf", "ssp", "tdlf", "tdlp", "tdsf", "tdsp")

#abbreviation <- quo(abbreviation)
abbreviation <- paste0("^(", paste(abbreviation, collapse="|"), ")")

select(db, matches(abbreviation)) # what should i do with this~
  

```





```{r}
results <- as.data.frame(all.columns) %>% 
  mutate(Discounting = as.character(all.columns),
         rsq = 1:n(),
         opt.lambda = 1:n()) %>% 
  select(-all.columns)

```



```{r}

y = db$average.consistent
x <- db %>% select(-one_of(all.columns)) %>% data.matrix()

lambdas <- 10^seq(3, -2, by = -.1)

fit <- glmnet(x, y, alpha = 0, lambda = lambdas)
cv_fit <- cv.glmnet(x, y, alpha = 0, lambda = lambdas)
plot(cv_fit)
opt_lambda <- cv_fit$lambda.min
opt_lambda
fit <- cv_fit$glmnet.fit


y_predicted <- predict(fit, s = opt_lambda, newx = x)

# Sum of Squares Total and Error
sst <- sum((y - mean(y))^2)
sse <- sum((y_predicted - y)^2)

# R squared
rsq <- 1 - sse / sst
rsq


```




```{r}
i=1
best_model_full <- NA
for (i in 1:nrow(results)){
  y = unlist(db[results[i,1]])
  x <- db %>% select(-one_of(all.columns)) %>% data.matrix()
  z <- x[1,]
  lambdas <- 10^seq(3, -2, by = -.1)
  
  fit <- glmnet(x, y, alpha = 0, lambda = lambdas)
  summary(fit)
  cv_fit <- cv.glmnet(x, y, alpha = 0, lambda = lambdas)
  plot(cv_fit)
  opt_lambda <- cv_fit$lambda.min
  results[i,3] <- opt_lambda # save
  fit <- cv_fit$glmnet.fit

  for (j in 1:nrow(db)){
    x1 <- t(x[j,] %>% as.matrix())
    y1 <- t(y[j] %>% as.matrix())
    
    y_predicted <- predict(fit, s = opt_lambda, newx = x1)
    
    # Sum of Squares Error
    sse <- sum((y_predicted - y[j])^2)
    
    # Save Results
    results[i,3+j] <- sse
    
  }



  y_predicted <- predict(fit, s = opt_lambda, newx = x)
  
  # Sum of Squares Total and Error
  sst <- sum((y - mean(y))^2)
  sse <- sum((y_predicted - y)^2)
  
  # R squared
  rsq <- 1 - sse / sst
  results[i,2] <- rsq
}

for (k in 1:nrow(db)){
  best_model <- results[which.min(results[,3+k]),1]
  best_model_full <- rbind(best_model_full, best_model)
}

best_model_full <- best_model_full[-1,] %>% as_tibble()
```





## Frquency for Model Fit
```{r}
best_model_full %>%
  group_by(value) %>% 
  summarise(Count = n()) %>% 
  arrange(Count = desc(Count)) %>% 
  ungroup() %>% 
  mutate(value = str_replace(value, abbreviation, taskname),
         value = str_replace(value, "td", "Time value"),
         value = str_replace(value, "ss.", "Speedup Small "),
         value = str_replace(value, "sl.", "Speedup Large "),
         value = proper(value),
         value = str_replace(value, "S.pa", " Speedup Pa")) %>% 
  mutate(value = str_replace(value, "discountings", "value Small "),
         value = str_replace(value, "discountingl.", "value Large "),
         value = str_trim(value),
         value = str_replace(value, "valuel.", "Value Large "),
         value = str_replace(value, ".indifference", " Factor "),
         value = str_replace(value, fixed("."), " "),
         value = str_replace(value, "Time value", "Time discounting "),
         value = proper(value)) %>%
  mutate(value = str_replace(value, "Time value", "Time discounting "),
        value = str_replace(value, "  ", " ")) %>% 
  ggplot(aes(reorder(value, -Count), Count))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(x = "Discounting Task", title = "Model Which Fits the Most People?")

ggsave("bestfit.png", bg = "transparent")
```





## Lowest RSQ
```{r}
rsqmodels <- results %>%
  select(Discounting, rsq) %>%
  arrange(desc(rsq)) %>% 
  mutate(Discounting = str_replace(Discounting, abbreviation, taskname),
         Discounting = str_replace(Discounting, "td", "Time Discounting"),
         Discounting = str_replace(Discounting, "ss.", "Speedup Small "),
         Discounting = str_replace(Discounting, "sl.", "Speedup Large "),
         Discounting = str_trim(Discounting),
         Discounting = proper(Discounting),
         Discounting = str_replace(Discounting, "S.pa", " Speedup Pa")) %>% 
  mutate(Discounting = str_replace(Discounting, "discountings", "Discounting Small "),
         Discounting = str_replace(Discounting, "discountingl.", "Discounting Large "),
         Discounting = str_replace(Discounting, ".indifference", " factor "),
         Discounting = str_trim(Discounting)) %>%
  mutate(Discounting = str_replace(Discounting, "Time value", "Time discounting "),
         Discounting = str_replace(Discounting, fixed("."), " "),
         Discounting = str_replace(Discounting, "  ", " ")) %>% 
  kable(format = "latex")

kable_as_image(rsqmodels, filename = "RSQ_table", latex_header_includes = NULL)
```



